% Based on https://github.com/sb2nov/resume

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://thefourtheye.in/}{\Large Sakthipriyan Vairamani}} & Email : \href{mailto:sakthi@thefourtheye.in}{sakthi@thefourtheye.in}\\
  \href{http://thefourtheye.in/}{http://thefourtheye.in} & Mobile : +91-999-460-2429 \\
\end{tabular*}

%-----------Key Features-----------------
\section{Key Features}
\resumeSubHeadingListStart
  \resumeSubheading
    {Node.js project's \href{} Technical Steering Committee Member}{}
    {\href{https://github.com/nodejs/TSC\#tsc-members}{List of TSC members and responsibilities}}{}
  \resumeSubheading
    {144,000+ reputation in stackoverflow}{}
    {\href{https://stackoverflow.com/users/1903116/thefourtheye}{Top 0.07\% of overall answerers}}{}
  \resumeSubheading
    {Chennai Node.js Meetup Organizer}{}
    {\href{https://www.meetup.com/nodejs-Chennai/}{One of the popular Node.js meetup groups in Chennai}}{}
\resumeSubHeadingListEnd

%-----------EXPERTISE-----------------
\section{Expertise}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Node.js}{}
      {One of the core contributors of the project.}{}
    \resumeSubheading
      {Python}{}
      {Both Python 2 and 3. Have knowledge about the internals of CPython implementation.}{}
    \resumeSubheading
      {Javascript}{}
      {Early adopter of new features. Good understanding of language specification and a little bit about V8 Engine.}{}
    \resumeSubheading
      {Java}{}
      {Eight+ years of professional development experience.}{}
    \resumeSubheading
      {Scala}{}
      {Love this language for the functional paradigm. Two+ years of professional development experience.}{}
    \resumeSubheading
      {C \& C++}{}
      {I use this in competitive programming. Six+ years of professional development experience.}{}  
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kamaraj College of Engineering \& Technology}{Virudhunagar, Tamilnadu, India}
      {Bachelor of Engineering in Computer Science;  72\%}{Aug. 2004 -- Jun. 2008}
      \resumeSubheading
      {K.V.S Higher Secondary School}{Virudhunagar, Tamilnadu, India}
      {+2;  89\%}{Jun. 2004}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {PayPal India Development Center}{Chennai, Tamilnadu, India}
      {Software Engineer 3}{Sep 2014 - Present}
      \resumeItemListStart
        \resumeItem{Crawler}
          {Internal application which crawls website from the internet and stores the result in files. Those files are used by different teams to do sentiment and market analyses.}
        \resumeItem{Kafka-ElasticSearch Pipeline}
          {This Akka streams based pipeline helps consuming data from Kafka and publishing them to ElasticSearch. This protects the ElasticSearch search with backpressure, if the cluster is slow or busy with some other tasks.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Science Corporation}{Chennai, Tamilnadu, India}
      {Software Engineer - for PayPal}{Dec 2011 - Sep 2014}
      \resumeItemListStart
        \resumeItem{Web Security}
          {Developed and integrated prevention frameworks with all the PayPal flows for common web attacks like CSRF and XSS.}
        \resumeItem{Anamoly Detection System}
          {Contributed to anamoly detection in the application layer, with respect to the number of requests and the type of requests. This helps greatly in preventing Account Take Overs.}
        \resumeItem{DDoS prevention for PayPal APIs}
          {Developed a system which would validate the API requests at different network layers to prevent DDoS attacks.}
      \resumeItemListEnd

    \resumeSubheading
      {Honeywell Technology Solutions}{Madurai, Tamilnadu, India}
      {Software Engineer}{Nov 2010 - Nov 2011}
      \resumeItemListStart
        \resumeItem{Turbobolt}
          {It is a bolted joint analysis program for the flight engine manufacturing system. It uses OpenGL to generate 3D models and XML as the datasource to store details about different materials.}
      \resumeItemListEnd

    \resumeSubheading
      {IBM India Private Limited}{Bengaluru, Karnataka, India}
      {Software Engineer}{Aug 2008 - Sep 2010}
      \resumeItemListStart
        \resumeItem{AT\&T Network Systems}
          {Worked on various projects which involve dealing with different network switches. Loading routing information to switches, bookkeeping of switches and changelogs, collecting performance information are few of the main aspects of these projects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
