% Based on https://github.com/sb2nov/resume

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://thefourtheye.in/}{\Large Sakthipriyan Vairamani}} & Email : \href{mailto:sakthi@thefourtheye.in}{sakthi@thefourtheye.in}\\
  \href{http://thefourtheye.in/}{http://thefourtheye.in} & Mobile : +91-999-460-2429 \\
\end{tabular*}

%-----------Key Features-----------------
\section{Key Features}
\resumeSubHeadingListStart
  \resumeSubheading
    {Node.js project's Technical Steering Committee Member}{}
    {\href{https://github.com/nodejs/TSC\#tsc-members}{List of TSC members and responsibilities}}{}
  \resumeSubheading
    {166,000+ reputation in stackoverflow}{}
    {\href{https://stackoverflow.com/users/1903116/thefourtheye}{Top 0.06\% of overall answerers}}{}
  \resumeSubheading
    {Chennai Node.js Meetup Organizer}{}
    {\href{https://www.meetup.com/nodejs-Chennai/}{One of the popular Node.js meetup groups in Chennai}}{}
\resumeSubHeadingListEnd

%-----------EXPERTISE-----------------
\section{Expertise}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Node.js}{}
      {One of the core contributors of the project.}{}
    \resumeSubheading
      {Python}{}
      {Both Python 2 and 3. Have a bit of knowledge about the internals of CPython implementation.}{}
    \resumeSubheading
      {Javascript}{}
      {Have a good understanding of the language and its specification. Also a little bit about V8 Engine.}{}
    \resumeSubheading
      {Java}{}
      {Eight+ years of professional development experience.}{}
    \resumeSubheading
      {C \& C++}{}
      {Used to use these in competitive programming. Have experience working with them in Node.js Core and CPython.}{}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kamaraj College of Engineering \& Technology}{Virudhunagar, Tamilnadu, India}
      {Bachelor of Engineering in Computer Science;  72\%}{Aug. 2004 -- Jun. 2008}
      \resumeSubheading
      {K.V.S Higher Secondary School}{Virudhunagar, Tamilnadu, India}
      {+2;  89\%}{Jun. 2004}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {PayPal India Development Center}{Chennai, Tamilnadu, India}
      {Software Engineer}{Sep 2014 - Present}
      \resumeItemListStart
        \resumeItem{FileVault}
          {This application is the port of PayPal. All external file transfers are done via this. Ensured that application is secure and refactored it for maintainability.}
        \resumeItem{Invoicing}
          {Refactored a huge chunk of critical parts of the Invoicing product for performance, readability, and memory leaks.}
        \resumeItem{Kafka-ElasticSearch Pipeline}
          {This Akka streams based pipeline helps consuming data from Kafka, with back pressure, and publishing them to ElasticSearch. One of the core developers of this product.}
        \resumeItem{Crawler}
          {Internal application which crawls websites from the internet. Improved the scalability of the application by reconstructing the core.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Science Corporation}{Chennai, Tamilnadu, India}
      {Software Engineer - for PayPal}{Dec 2011 - Sep 2014}
      \resumeItemListStart
        \resumeItem{Web Security}
          {Developed and integrated prevention frameworks with all the PayPal flows for common web attacks like CSRF and XSS.}
        \resumeItem{Anamoly Detection System}
          {Contributed to anamoly detection in the application layer, with respect to the number of requests and the type of requests. This helps greatly in preventing Account Take Overs.}
        \resumeItem{DDoS prevention for PayPal APIs}
          {Developed a system which would validate the API requests at different network layers to prevent DDoS attacks.}
      \resumeItemListEnd

    \resumeSubheading
      {Honeywell Technology Solutions}{Madurai, Tamilnadu, India}
      {Software Engineer}{Nov 2010 - Nov 2011}
      \resumeItemListStart
        \resumeItem{Turbobolt}
          {It is a bolted joint analysis program for the aeroplane engine manufacturing system. OpenGL was used to generate 3D models of the bolts.}
      \resumeItemListEnd

    \resumeSubheading
      {IBM India Private Limited}{Bengaluru, Karnataka, India}
      {Software Engineer}{Aug 2008 - Sep 2010}
      \resumeItemListStart
        \resumeItem{AT\&T Network Systems}
          {Managed various applications which deal with different network switches. Deploying routing information, bookkeeping of switches, and collecting performance information are few of the main aspects of these projects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
